\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{fontspec}

% Define your colors
\definecolor{myblue}{RGB}{33, 63, 127}
\definecolor{mygray}{RGB}{128, 128, 128}

% Set your page margins
\geometry{top=1in, bottom=1in, left=1in, right=1in}

% Define your header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

% Set your title
\title{\textcolor{myblue}{Internship Position Application \\[2ex] \large at Rijk Zwaan}}
\author{}
\date{\textcolor{myblue}{\today}}

\setmainfont{Comic Sans MS} % Set the main font to a fancy font

\begin{document}

\maketitle

Dear Committee members,
\\[3pt]

I am writing to express my sincere interest in the Internship in Biochemistry and AI, as advertised. The prospect of learning from you and contributing to your research team, while furthering my academic growth in the area of my keen interest, is incredibly exciting.

\section*{My Background}

I am a Uyghur who was born and raised in the Uyghur region of China. I earned my Bachelor's degree in biotechnology from Xinjiang University in China. Subsequently, I pursued my Master's degree in molecular diagnostics at the University of Camerino in Italy. Following my Master's, I had the opportunity to visit the Hebrew University of Jerusalem. Although I initially expected to pursue my Ph.D. in Europe and was accepted into the RNA Biology Lab at IMol, the Polish Academy of Sciences, challenges in obtaining a residence card in Poland due to various factors, coupled with the inability to return to China due to political issues affecting Uyghurs, led me to seek asylum in the Netherlands.

\section*{Motivation}
Nevertheless, I now have permission to work for a short period. This position aligns perfectly with my current situation, allowing me to leverage my skills and knowledge in a practical and impactful manner. In addition to my scientific background, I have a keen interest in AI and data analysis, with a basic understanding of image analysis and photography. Thank you for considering my application. I look forward to discussing the internship.

\textbf{Sincerely,}
\\[15pt]
\textcolor{myblue}{Yusufu Rouzimaimaiti (Yusup Rozimemet)\\
}

\end{document}